### 2022-05-16 readme.Rmd
I HAVE BROKEN THIS!

The approach uses quasi-random sampling to generate a quadrature
scheme based (e.g Berman & Turner 1992; Foster et al, 2018). Quasi-random 
sampling quadrature are form of spatially-balanced survey design or 
point stratification that aims to reduce the frequency of placing samples 
close to each other (relative to pseudo-random or grid designs). A quasi-random 
quadrature design improves efficiency of background point sampling 
(and subsequent modelling) by reducing the amount of spatial 
auto-correlation between data implying that each sample is providing as much 
unique information as possible (Grafston & Tille, 2013, Foster et al., 2018)
and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).
Because the quasi-random design is not on a regular grid we use a Dirichlet 
tessellation to generate polygons for each point. Areal weights are then derived
from these polygons.

>>>>

The approach uses quasi-random sampling (Grafston & Tille, 2013; Foster et
al, 2018) to generate a quadrature scheme for presence-only modelling 
(Berman & Turner 1992). Quasi-random sampling quadrature are form of spatially-
balanced survey design or point stratification that aims to reduce the frequency
of placing samples close to each other (relative to pseudo-random or grid 
designs). A quasi-random quadrature design improves efficiency of background 
point sampling (and subsequent modelling) by reducing the amount of spatial 
auto-correlation between data implying that each sample is providing as much 
unique information as possible (Grafston & Tille, 2013, Foster et al., 2018)
and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro,
2007). Because the quasi-random design is not on a regular grid we use a 
Dirichlet tessellation to generate polygons for each point. Areal weights are 
then derived from these polygons.
